\documentclass[main.tex]{subfiles}

\begin{document}

\subsection{Further results}
\label{ssc:further_results}

\begin{note}
  Toby: The remainder of this section consists of half-typed stuff I have at best sketched proofs of. I think that I have most of proof of \hyperref[thm:divide_by_marked_anodyne]{Theorem~\ref*{thm:divide_by_marked_anodyne}}. What is mainly missing is a proof the cocartesian marking always respects path components.
\end{note}

\begin{lemma}
  Let $f\colon X \to Y$ be a Reedy fibration between complete Segal spaces, and let $e \in X_{1}$ be a homotopy equivalence. Then $e$ is $f$-cocartesian. In particular, all identity morphisms are $f$-cocartesian.
\end{lemma}

\begin{lemma}
  \label{lemma:cocartesian_closed_under_composition}
  Let $f\colon X \to Y$ be a Reedy fibration between complete Segal spaces, and let $\sigma \in X_{2}$ be a 2-simplex as follows.
  \begin{equation*}
    \begin{tikzcd}[column sep=small]
      & y
      \arrow[dr, "g"]
      \\
      x
      \arrow[ur, "f"]
      \arrow[rr, swap, "h"]
      && z
    \end{tikzcd}
  \end{equation*}
  Then if $f$ and $g$ are $f$-cocartesian, so is $h$.
\end{lemma}

\begin{theorem}
  \label{thm:divide_by_marked_anodyne}
  Let $f\colon X \to Y$ be a cocartesian fibration of complete Segal spaces, and denote also by $f$ the morphism $f\colon X^{\natural} \to Y^{\sharp}$ as in \hyperref[def:cocoartesian_marking_on_complete_segal_spaces]{Definition~\ref*{def:cocoartesian_marking_on_complete_segal_spaces}}. Then for any marked anodyne morphism $u$, the map $\langle u \backslash f \rangle$ is a trivial fibration.
\end{theorem}

\begin{corollary}
  Let $f\colon X \to Y$ be a cocartesian fibration between complete Segal spaces. Then the corresponding map $f / \Delta^{0}$ between first rows is a cocartesian fibration of quasicategories.
\end{corollary}
\begin{proof}
  Since $\langle u \backslash f \rangle$ is a trivial fibration for any marked anodyne map $u\colon A \to A'$, we can solve the lifting problem
  \begin{equation*}
    \begin{tikzcd}
      \emptyset
      \arrow[r]
      \arrow[d]
      & A' \backslash X^{\natural}
      \arrow[d]
      \\
      \Delta^{0}
      \arrow[r]
      \arrow[ur, dashed]
      & A \backslash X^{\natural} \times_{A' \backslash Y^{\sharp}} A' \backslash Y^{\sharp}
    \end{tikzcd}.
  \end{equation*}

  This is equivalent to the lifting problem
  \begin{equation*}
    \begin{tikzcd}
      A
      \arrow[r]
      \arrow[d]
      & X^{\natural} / \Delta^{0}
      \arrow[d]
      \\
      A'
      \arrow[r]
      \arrow[ur, dashed]
      & Y^{\sharp} / \Delta^{0}
    \end{tikzcd}.
  \end{equation*}
  Thus, the map $f / \Delta^{0}$ has the right lifting property with respect to all marked anodyne morphisms and every morphism in $Y / \Delta^{0}$ is marked, which implies that the map $f / \Delta^{0}$ is a cocartesian fibration.
\end{proof}

\end{document}
